Physcraper: A Python package for continually updated phylogenetic trees using the Open Tree of Life

### 2021-04-01 sources/bmc_template_submission/bmc_article.tex
escape underscore

Physcraper generates gene trees, which individually do not capture the full complexity
of species' evolutionary history \cite{song2012resolving}.
However, Physcraper facilitates
gathering alignments and gene trees for multiple loci from a group of interest,
that together can be used to reconstruct species trees taking into account coalescent
processes with ASTRAL \cite{mirarab2014astral} or SVD Quartets \cite{chifman2014quartet}).
Rigorous analyses of multiple loci allows for more complex evolutionary models
than analyses of large genomic data sets, and can provide better evolutionary estimates.
For example \cite{zhu_complexity_2021} show that when applying coalescent models, there is more information in two genes of 300 bp each than in 600 independent sites
We have included a script ("multi_locus.py") and examples of how to automatically merge the outputs of Physcraper runs at different loci into input files for ASTRAL, SVD Quartets, or as concatenated alignments for concatenated analyses.

>>>>

Physcraper generates gene trees, which individually do not capture the full complexity
of species' evolutionary history \cite{song2012resolving}.
However, Physcraper facilitates
gathering alignments and gene trees for multiple loci from a group of interest,
that together can be used to reconstruct species trees taking into account coalescent
processes with ASTRAL \cite{mirarab2014astral} or SVD Quartets \cite{chifman2014quartet}).
Rigorous analyses of multiple loci allows for more complex evolutionary models
than analyses of large genomic data sets, and can provide better evolutionary estimates.

For example \cite{zhu_complexity_2021} show that when applying coalescent models, there is more information in two genes of 300 bp each than in 600 independent sites 
We have included a script (``multi\_locus.py'') and examples of how to automatically merge the outputs of Physcraper runs at different loci into input files for ASTRAL, SVD Quartets, or as concatenated alignments for concatenated analyses.
